### 2013-10-08 src2/thesis.tex
update

@@

@@

@@

% --------------------------------------------------------------------------- %
% --------------------------------------------------------------------------- %
%
%  INTRODUCTION 
%
% --------------------------------------------------------------------------- %
% --------------------------------------------------------------------------- %
\chapter{Introduction}

\section{The scope}

@@

\noindent\emph{GPUs}

\noindent\emph{The context, Lift head from details}

@@

\section{The method}

>>>>

The first real paper about Obsidian, our embedded language for GPU 
programming. In this paper we identify similarities between 
conenction patterns in hardware and parallel computations on GPUs. 
We introduce a structured and compositional way to write data-parallel 
programs on a GPU.

Basic parallel building blocks are implemented in a monadic style and 
composed using a sequential composition operator {\tt ->-}.

@@

\emph{a new program representation, based vaguely on Arrows}

@@

This paper introduces {\em Push} arrays, invented by Koen Claessen. This 
array representation target specific performance problems that we want 
to solve with Obsidian.

@@

% --------------------------------------------------------------------------- %
% --------------------------------------------------------------------------- %
%
%  INTRODUCTION 
%
% --------------------------------------------------------------------------- %
% --------------------------------------------------------------------------- %
\chapter{\thesistitle}

\section{Introduction}

Computers today are increasingly parallel. With each new generation of 
general purpose processor or GPU we get more parallel resources. To 
fully make use of modern CPUs and GPUs we need to fully exploit their 
parallelism.

Modern CPUs are parallel in a number of different ways. They discover instruction
level parallelism(ILP), they have multiple processor cores and vector units for 
Single Instruction Multiple Data parallelism. The exact configurations, number
of cores and number of vector units, vary over available processors.

\noindent\emph{More text, lead into something about ArBB and forward ref to ArBB papers}

@@

Graphics Processors (GPUs), trade programmer convenience for increased parallelism. 
For example, where CPUs dedicate much chip real estate for caches, branch prediction and 
ILP, GPUs put additional cores. This comes at a price of increased programmer effort.
GPUs have programmer managed shared memories, conditionals are troublesome from a performance 
perspective and memory access patterns can make or break the performance of an 
application.

\noindent\emph{More text, lead into something about compositional, high-level, but 
expressive enough programming models for GPU programming and ref to Obsidian Chapter}

%\noindent\emph{GPUs}

%\subsection{Data-parallel programming on GPUs}

%\subsection{Data-parallel programming on CPUs}

@@

\section{An embedded languages approach to data-parallelism}
